Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
did more

```{r Plot How Many Topics}
# Plot results to determine the optimal number of topics
FindTopicsNumber_plot(result)
```

@@

```{r Improved Co-occurrence Network Analysis}
library(ggforce)
library(ggrepel)
library(ggplot2)
library(igraph)

@@

# Emotional Tone Hypothesis

# Author Impact Hypothesis

>>>>

```{r Plot How Many Topics, eval=FALSE, include=FALSE}
# Plot results to determine the optimal number of topics
FindTopicsNumber_plot(result)
```
Six Topics!

@@

```{r Co-occurrence Network Analysis}
library(ggforce)
library(ggrepel)
library(ggplot2)
library(igraph)

@@

# Emotional Tone Hypothesis
```{r Load All Datasets}
usenet_comments_all <- read.csv(file.path(comments_directory, "combined_comments_cleaned_82TO86.csv"))
usenet_threads_all  <- read.csv(file.path(threads_directory, "combined_threads_cleaned_82TO86.csv"))
```

```{r Descriptive Statistics Related to Sentiment}
library(moments)

# Calculate descriptive statistics for AIDS-related discussions
aids_sentiment_stats <- filtered_comments %>%
  summarize(
    Min = min(SentimentScore, na.rm = TRUE),
    Max = max(SentimentScore, na.rm = TRUE),
    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
    Mean = mean(SentimentScore, na.rm = TRUE),
    Median = median(SentimentScore, na.rm = TRUE),
    SD = sd(SentimentScore, na.rm = TRUE),
    Skewness = skewness(SentimentScore, na.rm = TRUE),
    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
  ) %>%
  mutate(Dataset = "Dataset Three")

# Calculate descriptive statistics for the entire Usenet dataset
usenet_sentiment_stats <- usenet_comments_all %>%
  summarize(
    Min = min(SentimentScore, na.rm = TRUE),
    Max = max(SentimentScore, na.rm = TRUE),
    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
    Mean = mean(SentimentScore, na.rm = TRUE),
    Median = median(SentimentScore, na.rm = TRUE),
    SD = sd(SentimentScore, na.rm = TRUE),
    Skewness = skewness(SentimentScore, na.rm = TRUE),
    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
  ) %>%
  mutate(Dataset = "Dataset One")

# Combine the descriptive statistics into one table
combined_sentiment_stats <- bind_rows(aids_sentiment_stats, usenet_sentiment_stats) %>%
  select(Dataset, everything())  # Ensure 'Dataset' column is the first column

combined_sentiment_stats
```

```{r Identify Influential Authors by Number of Connections}
# Load necessary libraries
library(dplyr)
library(igraph)

# Step 1: Create an edge list based on co-participation in threads
edges <- filtered_comments %>%
  filter(Thread.ID != "") %>%  # Ensure Thread.ID is not empty
  group_by(Thread.ID) %>%
  filter(n() > 1) %>%  # Only consider threads with more than one comment
  summarize(edgelist = list(combn(Author, 2, simplify = FALSE))) %>%  # Create pairwise combinations of authors
  unnest(edgelist) %>%
  unnest_wider(edgelist, names_sep = "") %>%
  rename(source = edgelist1, target = edgelist2) %>%
  filter(source != target) %>%  # Remove self-loops
  group_by(source, target) %>%
  summarize(weight = n(), .groups = 'drop')  # Count the number of co-participations as edge weight

# Step 2: Create a graph object from the edge list
graph <- igraph::graph_from_data_frame(edges, directed = FALSE)

# Step 3: Calculate the degree (number of connections) for each author
author_influence <- data.frame(
  Author = igraph::V(graph)$name,
  Influence = igraph::degree(graph)
)

# Step 4: Identify the top 15 most influential authors
top_influential_authors <- author_influence %>%
  arrange(desc(Influence)) %>%  # Sort authors by descending influence
  slice(1:15)  # Select the top 15 authors

# Display the list of top 15 influential authors
print(top_influential_authors)
```

```{r Calculate and Print Author Influence on Sentiment Scores}
# Filter the all_comments dataset to only include posts by the top 15 influential authors
top_authors_comments <- filtered_comments %>%
  filter(Author %in% top_influential_authors$Author)

# Calculate descriptive statistics for the sentiment scores of influential authors
influential_authors_sentiment_stats <- top_authors_comments %>%
  summarize(
    Min = min(SentimentScore, na.rm = TRUE),
    Max = max(SentimentScore, na.rm = TRUE),
    Range = max(SentimentScore, na.rm = TRUE) - min(SentimentScore, na.rm = TRUE),
    Mean = mean(SentimentScore, na.rm = TRUE),
    Median = median(SentimentScore, na.rm = TRUE),
    SD = sd(SentimentScore, na.rm = TRUE),
    Skewness = skewness(SentimentScore, na.rm = TRUE),
    Kurtosis = kurtosis(SentimentScore, na.rm = TRUE)
  ) %>%
  mutate(Dataset = "Influential Authors")

# Combine the sentiment statistics into one table
combined_sentiment_stats <- bind_rows(
  aids_sentiment_stats,  # AIDS-related discussions
  usenet_sentiment_stats,  # Entire Usenet dataset
  influential_authors_sentiment_stats  # Influential authors
) %>%
  select(Dataset, everything())  # Ensure 'Dataset' column is the first column

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "sentiment_score_descriptive_statistics_combined.html")

combined_sentiment_stats

# Display the combined descriptive statistics table using sjPlot
tab_df(
  combined_sentiment_stats,
  title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
  show.rownames = FALSE,
  show.ci = FALSE,
  show.p = FALSE,
  digits = 2,
  file = output_file_path)
```

```{r Time Series Plot of Sentiment Scores}
# Ensure necessary libraries are loaded
library(ggplot2)
library(dplyr)

# Convert Date columns to Date type
filtered_comments$Date <- as.Date(filtered_comments$Date)
usenet_comments_all$Date <- as.Date(usenet_comments_all$Date)

# Calculate monthly average sentiment scores for AIDS-related discussions
monthly_sentiment_aids <- filtered_comments %>%
  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))

# Calculate monthly average sentiment scores for the entire Usenet dataset
monthly_sentiment_usenet <- usenet_comments_all %>%
  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))

# Filter the all_comments dataset to only include posts by the top 15 influential authors
top_authors_comments <- filtered_comments %>%
  filter(Author %in% top_influential_authors$Author)

# Calculate monthly average sentiment scores for the influential authors
monthly_sentiment_influential <- top_authors_comments %>%
  group_by(Month = as.Date(format(Date, "%Y-%m-01"))) %>%
  summarize(AverageSentiment = mean(SentimentScore, na.rm = TRUE))

# Combine the datasets for plotting
combined_monthly_sentiment <- bind_rows(
  monthly_sentiment_usenet %>% mutate(Dataset = "Dataset One"),
  monthly_sentiment_aids %>% mutate(Dataset = "Dataset Three"),
  monthly_sentiment_influential %>% mutate(Dataset = "Influential Authors")
)

# Create the time series plot with a white background and no legend title
time_series_plot <- ggplot(combined_monthly_sentiment, aes(x = Month, y = AverageSentiment, color = Dataset)) +
  geom_line(size = 1.2) +
  labs(
    title = "Time Series of Average Sentiment Scores Over Time",
    x = "Month",
    y = "Average Sentiment Score"
  ) +
  theme_bw() +  # Use theme_bw() for a white background
  theme(legend.position = "bottom") +
  guides(color = guide_legend(title = NULL))  # Remove the legend title

# Print the plot to the R console
print(time_series_plot)

# Save the plot to a PNG file
output_file_path <- file.path(output_directory, "images and tables", "time_series_sentiment_plot.png")
ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
```

# Author Impact Hypothesis
```{r LDA Model for Influential Authors}
# Prepare the corpus for influential authors
influential_corpus <- Corpus(VectorSource(top_authors_comments$Full.Text))
influential_corpus <- tm_map(influential_corpus, content_transformer(tolower))
influential_corpus <- tm_map(influential_corpus, removePunctuation)
influential_corpus <- tm_map(influential_corpus, removeNumbers)
influential_corpus <- tm_map(influential_corpus, removeWords, stopwords("english"))
influential_corpus <- tm_map(influential_corpus, stripWhitespace)

# Create DTM for influential authors
influential_dtm <- DocumentTermMatrix(influential_corpus)
influential_dtm <- removeSparseTerms(influential_dtm, 0.90)
```

```{r How Many Topics}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  influential_dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
  mc.cores = 2L,
  verbose = TRUE
)

# Plot results to determine the optimal number of topics
FindTopicsNumber_plot(result)
```

```{r LDA Model and Top Terms}
# LDA for influential authors
set.seed(123)
influential_lda <- LDA(influential_dtm, k = 6, control = list(seed = 123))

# Load required libraries
library(tidyr)
library(dplyr)
library(sjPlot)

# Visualize the top terms for each topic (concise visualization)
influential_topics <- tidy(influential_lda, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Round beta values to 3 decimal places
influential_topics <- influential_topics %>%
  mutate(beta = round(beta, 3))

# Reshape the data frame to have each topic's terms and betas side by side
reshaped_df <- influential_topics %>%
  group_by(topic) %>%
  mutate(term_id = row_number()) %>%
  ungroup() %>%
  pivot_wider(
    names_from = topic,
    values_from = c(term, beta),
    names_glue = "Topic_{topic}_{.value}"
  )

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "Top Terms and Betas for Each Topic (Influential Authors).html")
gtsave(gt_table, output_file_path)
```

```{r Topic Matching}
# Extract top terms from the overall LDA model (assuming it's stored in 'lda_model')
overall_topics <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Function to calculate Jaccard similarity
jaccard_similarity <- function(set1, set2) {
  intersection <- length(intersect(set1, set2))
  union <- length(union(set1, set2))
  return(intersection / union)
}

# Compare topics
topic_similarities <- data.frame(
  Influential_Topic = numeric(),
  Overall_Topic = numeric(),
  Similarity = numeric()
)

for (i in 1:6) {
  influential_terms <- influential_topics %>% filter(topic == i) %>% pull(term)
  for (j in 1:6) {
    overall_terms <- overall_topics %>% filter(topic == j) %>% pull(term)
    similarity <- jaccard_similarity(influential_terms, overall_terms)
    topic_similarities <- rbind(topic_similarities, data.frame(
      Influential_Topic = i,
      Overall_Topic = j,
      Similarity = similarity
    ))
  }
}

# Find the best matching topics
best_matches <- topic_similarities %>%
  group_by(Influential_Topic) %>%
  slice_max(order_by = Similarity, n = 1)

tab_df(best_matches)
```

```{r Similarity Plot}
library(ggplot2)

ggplot(best_matches, aes(x = factor(Influential_Topic), y = Similarity, fill = factor(Overall_Topic))) +
  geom_bar(stat = "identity") +
  labs(title = "Similarity Between Influential Authors' Topics and Overall Topics",
       x = "Influential Authors' Topic",
       y = "Jaccard Similarity",
       fill = "Best Matching Overall Topic") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(file.path(output_directory, "images and tables", "topic_influence_comparison.png"), 
       width = 10, height = 6, dpi = 300)
```
